MINOS Handover Plots

### 2024-05-16 minos/validation/handovers.Rmd
Small tweak to child_ages plot to get the factor level labels right

@@

ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

>>>>

combined$expanded_child_ages <- factor(combined$expanded_child_ages,
                                       levels = c('0', '1', '2', '3', '4', '5', 
                                                  '6', '7', '8', '9', '10', 
                                                  '11', '12', '13', '14', '15', 
                                                  '16', 'childless'))

@@

ggplot(data = combined, mapping = aes(x = expanded_child_ages, y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Age') +
  ylab('Count')
